Neural correlates of the deployment of spatial attention, and their modulation by repetitive movements

### 2024-07-23 manuscript.qmd
Updated about bayes factors

Raw EEG data were converted into EEGlab .set format using Matlab and the EEGlab toolbox [@Delorme2004]. We then used MNE python for the main analysis. Data were bandpass filtered between 0.2 and 30Hz, and then epoched using the event timestamps. We performed classification using a linear classifier with 10-fold cross-validation on the voltage data across all electrodes (excluding electrodes *M1* and *M2*), independently at each time point and for each participant. We then averaged classification accuracy across participants to generate the timecourses used in the main analysis. We calculate Bayes factors [@Rouder2009] to compare classification accuracy to chance performance (50\% correct) and to make between conditions and groups, but also report frequentist tests for comparison. We express Bayes factors in logarithmic units to account for extreme values

>>>>

Raw EEG data were converted into EEGlab .set format using Matlab and the EEGlab toolbox [@Delorme2004]. We then used MNE python for the main analysis. Data were bandpass filtered between 0.2 and 30Hz, and then epoched using the event timestamps. We performed classification using a linear classifier with 10-fold cross-validation on the voltage data across all electrodes (excluding electrodes *M1* and *M2*), independently at each time point and for each participant. We then averaged classification accuracy across participants to generate the timecourses used in the main analysis. We calculate Bayes factors [@Rouder2009] to compare classification accuracy to chance performance (50\% correct) and to make between conditions and groups, but also report frequentist tests for comparison. We express Bayes factors in logarithmic units to account for extreme values ($log_{10}BF_{10}$), such that a Bayes factor of 3 is a $log_{10}BF_{10}$ = `r round(log10(3),digits=2)`, and constitutes convincing evidence for the alternative hypothesis, a Bayes factor of 10 is a $log_{10}BF_{10}$ = `r round(log10(10),digits=2)`, and constitutes strong evidence for the alternative hypothesis, and a Bayes factor of 30 is a $log_{10}BF_{10}$ = `r round(log10(30),digits=2)`, and constitutes overwhelming evidence for the alternative hypothesis.
